A Horrocks-type theorem for even orthogonal $K_2$

### 2019-09-25 dl-paper.tex
Minor

\begin{rem}\label{Z-DS} Notice that our assumptions on the rank of $\Phi$ guarantee that $Z_0(\alpha)$ is nonempty, hence the group $Z_\alpha(A, M)$ contains relative Dennis--Stein symbols $\langle a, m \rangle$ for $a\in A$, $m\in M$.
By~\eqref{DS-S-relationship} relative Steinberg symbols $\{a, 1+m\}$ are also contained in $Z_\alpha(A, M)$ for all $a\in A^\times$, $m\in M$. \end{rem}

\begin{df} \label{defP0}
Let $M$ be an ideal of a local ring $A$. We denote by $P_{\alpha, M}(0)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by the images of the following elements of $\St(\Phi, A[X])$ under the
 map $j_+ \colon \overline{\St}(\Phi, A[X], M[X]) \to \St(\Phi, A[X, X^{-1}])$:
\begin{enumerate} \item $z_{\beta}(Xf, \xi), \beta \in \Phi \text{ such that }\alpha + \beta \in \Phi\text{ or } \alpha - \beta \in \Phi;$
 \item $z_{\beta}(f, X\xi),\ \alpha - \beta \in \Phi;$
 \item $z_{\beta}(f, \xi),\ \beta \perp \alpha;$
 \item $x_{-\alpha}(X^2f);$
 \item $x_{\alpha}(f)$. \end{enumerate}
In the above formulae and for the rest of this subsection $f \in M[X]$ and $\xi \in A[X]$.

@@

\begin{rem}\label{rem:c-DS} It is easy to check that $P_{\alpha, M}(0)$ contains the image of $Z_\alpha(A, M)$ under the natural embedding of $\St(\Phi, A, M) \hookrightarrow \St(\Phi, A[X, X\inv])$.
In particular, it contains the relative Dennis--Stein and Steinberg symbols.
Notice that $P_\alpha(0)$ also contains the elements $c_{\beta}(f, X\xi)$ for all $\beta \in Z(\alpha)$ (they can be factored as products of two elements of type 2 or 3). \end{rem}

>>>>

\begin{rem}\label{Z-DS} Notice that our assumptions on the rank of $\Phi$ guarantee that $Z_0(\alpha)$ is nonempty. In particular, if $A$ is a local ring with maximal ideal $M$ the group $Z_\alpha(A, M)$ contains relative Dennis--Stein symbols $\langle a, m \rangle$ for $a\in A$, $m\in M$.
By~\eqref{DS-S-relationship} relative Steinberg symbols $\{a, 1+m\}$ are also contained in $Z_\alpha(A, M)$ for all $a\in A^\times$, $m\in M$. \end{rem}

\begin{df} \label{defP0}
Let $M$ be an ideal of a local ring $A$. We denote by $P_{\alpha, M}(0)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by the images of the following elements of $\overline{\St}(\Phi, A[X], M[X])$ under the map $j_+ \colon \St(\Phi, A[X]) \to \St(\Phi, A[X, X^{-1}])$:
\begin{enumerate} \item $z_{\beta}(Xf, \xi),\ \beta \in \Phi \text{ such that }\alpha + \beta \in \Phi\text{ or } \alpha - \beta \in \Phi;$
 \item $z_{\beta}(f, X\xi),\ \alpha - \beta \in \Phi;$
 \item $z_{\beta}(f, \xi),\ \beta \perp \alpha;$
 \item $x_{-\alpha}(X^2f);$
 \item $x_{\alpha}(f)$. \end{enumerate}
In the above formulae and for the rest of this subsection $f \in M[X]$ and $\xi \in A[X]$.

@@

\begin{rem}\label{rem:c-DS} Notice that $P_{\alpha, M}(0)$ contains the elements $c_{\beta}(f, X\xi)$ for all $\beta \in Z(\alpha)$ (they can be factored as products of two elements of type 2 or 3). It is also easy to check that $P_{\alpha, M}(0)$ contains the image of $Z_\alpha(A, M)$ under the natural embedding of $\St(\Phi, A, M) \hookrightarrow \St(\Phi, A[X, X\inv])$.
In particular, if $M$ is the maximal ideal of $A$, the subgroup $P_{\alpha, M}(0)$ contains relative Dennis--Stein and Steinberg symbols. \end{rem}
